\section{Theoretical constructs}
\subsection{The main principles of classical lattice models}
Let $\Omega$ be a finite set (the set of \emph{microstates}), let $\hh : \Omega \rightarrow \mathbb R$ be a \emph{hamiltonian}, a specifically chosen random variable. Let $\mathcal M(\Omega)$ be the space of probability measures on $\Omega$. In this theory, the expectation of a random variable $f : \Omega \rightarrow \mathbb R$ with respect to a measure $\mu$ (if not implicitly understood; it's also called the \emph{thermal average}) is denoted as
\[
\left\langle f \right\rangle_{\mu} := \mathbb E_{\mu} f = \int_{\Omega} f d\mu.
\]
One of the first questions in statistical mechanics is devoted to the choice of the right measure $\mu$. The choice is governed by Shannon's entropy $S : \mathcal M(\Omega) \rightarrow \mathbb R$, defined as $S(\mu) := -\int_{\Omega}x\log x d\mu(x)$ (there's a way to understand why $S$ has this form; see \cite{friedli}). \emph{The maximum entropy principle says}: for a given model of statistical mechanics, choose $\mu$ that maximizes $S$. For example, if there's no other information available about the system, then the measure that maximizes $S$ is the uniform distribution. There are other two typical situations:
\begin{enumerate}[(a)]
\item If we know that $\left\langle \mathcal H\right\rangle = U$ for some fixed $U$ (the \emph{internal energy} of the system), then the measure that maximizes $S$ is 
\[
\mu(\omega) = \frac{e^{-\beta H(\omega)}}{Z}, \ \ Z:= \sum_{\omega \in \Omega} e^{-\beta \mathcal H(\omega)} 
\]
which is the \emph{Gibbs measure}. As the condition says, we either know the system is isolated, or we know the system exchanges its energy with the external environment but on average the internal energy is preserved. The result can be obtained using Lagrange multipliers; the parameter $\beta$, called the \emph{inverse temperature}, is uniquely determined by $U$ (and vice versa: $U$ is uniquely determined by $\beta$). In the theory, $\beta = (kT)^{-1}$, where $k$ is the Boltzmann constant and $T$ is the temperature of the system.
\item If we know additionally that the system exchanges its particles $\mathcal N$ with the external environment, and that the expected value of the particles if $\left\langle \mathcal N \right\rangle = N$, then we obtain a \emph{grand canonical Gibbs distribution} via a similar procedure. It's given by
\[
\mu(\omega) := \frac{e^{-\beta(\hh(\omega)-\mu N)}}{Z}, \ \ Z := \sum_{N} e^{\beta \mu N} \sum_{\omega \in \Omega} e^{-\beta \hh (\omega)}.
\]
The parameter $\mu$ is identified with the so-called \emph{chemical potential}.
\end{enumerate}

\subsection{The thermodynamic limit}

\subsection{Quantum lattices}
\subsubsection{A general set-up}
I will follow closely the treatment in \cite{israel}. Again, we have a lattice $X \subset \mathbb Z^n$, but to each site $i \in X$ we attach a copy of a finite-dimensional Hilbert space $H_i$. To a finite $X$ we attach the tensor product $H_X := \otimes_{i \in X} H_i$. %For example, in spin-$1/2$ systems each Hilbert space is two-dimensional, with an orthonormal basis corresponding to spins up and down.

For infinite lattices, the author of \cite{israel} suggests proceeding as follows. Let $\mathfrak{A}_X := \End(H_X)$, and for any two finite subsets $X \subseteq Y \subset \mathbb Z^n$, let $\imath : \mathfrak{A}_X \rightarrow \mathfrak{A}_Y$ be the inclusion that sends $A$ to $A \otimes 1$ (where $1$ is viewed as an endomorphism of $\mathfrak{A}_{Y\setminus X}$). For an infinite $\Lambda \subseteq \mathbb Z^n$, the family of all its finite subsets with the inclusions form a direct system. Let $\mathfrak A_{\Lambda} := \varinjlim \mathfrak{A}_X$ be the direct limit taken in the category of $C^*$-algebras over all finite subsets of $\Lambda$. In the literature, this algebra is known as an AF (approximately finite-dimensional) $C^*$-algebra. The first reference in this theory goes back to Bratteli \cite{bratteli}. See the next subsection for an elaboration on the inductive limit.

Further, for a finite $\Lambda \subset \mathbb Z^n$ and a Hamiltonian $\mathcal H_{\Lambda}$, the partition function is defined as
\[
Z = \tr_{\Lambda} e^{-\beta \mathcal H_{\Lambda}}
\]
and the expectation of an observable $A \in \mathfrak A_{\Lambda}$ is 
\[
\left\langle A \right\rangle_{\Lambda} := Z^{-1} \tr_{\Lambda} (A e^{-\mathcal H_{\Lambda}}).
\]
The trace in these formulas is normalized: it's $1/d$ of the usual trace, where $d$ is the dimension of the Hilbert space at one site. An interesting consequence of such normalization is that $\tr$ extends than to a norm-one linear functional on the whole $\mathfrak A:= \mathfrak A_{\mathbb Z^n}$ (see \cite{israel}). The Hamiltonian they choose is given by
\[
\mathcal H_{\Lambda} = \sum_{X \subseteq \Lambda} \Phi(X),
\]
where $\Phi$ is a so-called \emph{interaction}: it's a function from the non-empty finite subsets of $\mathbb Z^n$ to self-adjoint operators on them, such that $\Phi(X+i) = \Phi(X)$ for any $i \in \mathbb Z^n$ (i.e., it's translational invariant).

The pressure for a finite region $\Lambda$ in the quantum lattice system is given by
\[
P_{\Lambda}(\Phi) := |\Lambda|^{-1} \ln \tr e^{-H_{\Lambda}}.
\]
One can show that the limit in the sense of van Hove of $P_{\Lambda}$ does exist in the quantum setting as well (\cite{israel}).

%\begin{fur}
%Not yet have I delved into the properties of AF $C^*$-algebras. How is the norm defined there at least? Not yet clear.
%\end{fur}
%
%\begin{fur}
%It's said in \cite{bratteli} that one might refer to \cite{haag} for limits of lattices in case the number of states is infinite.
%\end{fur}
\subsubsection{The inductive limit in more detail}
For two finite subsets $X \subseteq Y \subset \mathbb Z^n$, the inclusion $\imath : \mathfrak A_{X} \rightarrow \mathfrak A_{Y}$ that sends $A$ to $A \otimes 1$ is injective; therefore, whenever $X \subseteq Y$, we can view $\mathfrak A_{X}$ as a subalgebra of $\mathfrak A_{Y}$. Hence we can take a union of all such subalgebras coming from finite subsets of $\Lambda \subseteq \mathbb Z^n$, and then, to be safe and ensure it's a Banach space, take the closure. So, one can identify (see a proposition below for a rigorous proof)
\[
\mathfrak A_{\Lambda} = \varinjlim \mathfrak A_{X} = \cl \left(\bigcup_{X \subset \Lambda, \ |X| < \infty} \mathfrak A_{X}\right)/_{u \sim u \otimes 1}
\]
From this point of view, it's easy to understand what the norm is. For $A$ from the dense subspace (the union itself), we just set $\|A\|_{\Lambda} := \|A\|_{X}$ if $A \in \mathfrak A_{X}$. The norm extends to the closure by the very process of completeness: for $A \in \mathfrak A_{\Lambda}$, we choose a sequence $A_n \in \mathfrak A_{X_n}$ such that $A_n \rightarrow A$, and then set $\|A\|_{\Lambda} := \lim_{n \rightarrow \infty} \|A_n\|$.

From Appendix on $C^*$-algebras, we see that Gelfand-Naymark theorem ensures there is a Hilbert space $H$ such that $\mathfrak A_{\Lambda} \cong \End(H)$.
\begin{fur}
I can elaborate on the construction of this Hilbert space. It's more or less constructive and relies on finding pure states. In particular, it would be interesting to see how this $H$ is related to the infinite tensor product $\otimes_{i \in \Lambda} H_i$: what exactly goes wrong?
\end{fur}
\begin{proposition}
In the above set-up, we indeed have $\varinjlim \mathfrak A_{X} = \cl \left(\bigcup_{X \subset \Lambda, \ |X| < \infty} \mathfrak A_{X}\right)/_{u \sim u \otimes 1}$ (isometrically and preserving the $\ast$-structure).
\end{proposition}
\begin{proof}
Denote $\mathfrak A^\prime := \left(\bigcup_{X \subset \Lambda, \ |X|<\infty} \mathfrak A_X\right)/_{u \sim u \otimes 1}$.
So, we choose morphisms in the category of unital $C^*$-algebras as bounded unital $\ast$-homomorphisms with norm less then or equal to one\footnote{Otherwise I don't think there's a way to prove that the map induced on the diagram of the injective limit is a bounded operator}. To prove the statement, all we need to show is that for a unital $C^*$-algebra $A$ and a bunch of morphisms $\alpha_X : \mathfrak A_X \rightarrow \mathfrak A_Y$ where $X \subseteq Y$ and such that $\alpha_X(u) = \alpha_Y(u \otimes 1)$ (but remember that $u$ is identified with $u \otimes 1$ in the union), there's a unique morphism $\alpha : \cl \mathfrak A^\prime \rightarrow A$. In the language of diagrams, this is saying that
\[
\xymatrix{
& & A & & \\
& &  & & \\
& & \cl \mathfrak A^\prime\ar@{-->}[uu]_{\exists ! \alpha} & &\\
\mathfrak A_X\ar[rrrr]^{u \mapsto u \otimes 1} \ar[rru]^{\imath_X} \ar[rruuu]^{\alpha_X} & & & & \mathfrak A_Y\ar[lluuu]_{\alpha_Y} \ar[llu]_{\imath_Y}
}
\]
Once $\alpha$ is defined on $\mathfrak A^\prime$ with all the mentioned properties, it automatically extends to the closure. So, for $u \in \mathfrak A_X$ we set $\alpha(u) := \alpha_X(u)$. This is well defined, for $u$ is identified with $u \otimes 1$ in the union. We get automatically that $\alpha$ is a unital $\ast$-homorphism since all $\alpha_X$'s are. It's norm is bounded by $1$, for $\|\alpha(u)\| \leq \|\alpha_X\|\|u\| \leq \|u\|$. Thus $\alpha$ is a morphism in the corresponding category.
\end{proof}

\begin{ths}
So, any element of the union itself can be interpreted as an observable on some finite lattice. But when we take the closure of the union, we get infinite sums of operators. The very procedure of the closure is not attached to the nature of the operators (i.e. than they can be fed with states) but only to the relation between operators themselves. Therefore, we need to define what is $\sum_{n=1}^\infty A_n (x)$ for $A_n \in \mathfrak A_{X_n}$. An attempt to fantasy is: for $x \in H_{\Lambda}$, let $\pi_n(x)$ be the projection of $x$ to $H_{X_n}$ ($H_{X_n}$ can be regarded as a subspace of $H_{\Lambda}$). Then we try to set $(\sum A_{n})(x):= \sum A_n(\pi_n(x))$. Then $\sum A_{n}$ is a bounded linear operator, for $\|\sum A_n(\pi_n(x))\| \leq (\sum \|A_n\|)\|x\|$. Hmm, why don't we like it? And yet, what's the difference between this and the G-N theorem? Are there fewer operators than in $\End(H_{\Lambda})$?
\end{ths}

\subsection{Relation between classical and quantum lattices}
I follow \cite{israel} with some minor modifications more appealing to my taste. Let $\Omega_0$ be a finite set of microstates at one site, and let $H_0$ be a Hilbert space of dimension equal to $|\Omega|$ (which is assigned to one site as well). Let $C(\Omega)$ be the space of observables on $\Omega$. Choose an orthonormal basis $e_{\mu}$ of $H_0$ labeled my microstates $\mu \in \Omega_0$. Then we have an injection $\imath : C(\Omega_0) \rightarrow \End(H_0)$ given by
\[
[\imath(f)](e_{\mu}) := e_{f(\mu)}.
\]
In other words, the classical observables are embedded into the quantum observables as diagonal matrices.

\subsection{Continuous spins: general principles}\label{ss:gen_princ}
I follow closely Section 6.10 of \cite{friedli}. In case the space of states $\Omega_0$ at a single site is non-compact, the existence of Gibbs measures is no longer guaranteed. For $\Omega_0$ a topological space, one defines the following ingredients. Let $\mathcal B_0$ be the Borel $\sigma$-algebra on $\Omega_0$. For a finite lattice $\Lambda \subset \mathbb Z^n$, we supply the space of states with the $\sigma$-algebra $\mathcal B_{\Lambda} := \bigotimes_{i \in \Lambda} \mathcal B_0$. The natural projections $\pi_{\Lambda} : \Omega \rightarrow \Omega_{\Lambda}$ allow us to define a $\sigma$-algebra on $\Omega$ with base in $\Lambda$:
\[
\sigma_{\Lambda} := \pi^{-1}_{\Lambda}(\mathcal B_{\Lambda}).
\]
If $S \subseteq \mathbb Z^n$ is a possibly infinite lattice, then we supply it with the $\sigma$-algebra
\[
\sigma_{S} := \sigma(\bigcup_{\Lambda \subset S, \ \Lambda \text{ finite}} \sigma_{\Lambda})
\]
(by the last equality I mean the smallest $\sigma$-algebra generated by the union).

\subsection{Rigged Hilbert spaces}
For this subject, I read Antoine's notes \cite{antoine} (but they are more on lattices of Hilbert spaces, which is a further extension of rigged Hilbert spaces). I also read Section \textsection 4 from Chapter 1 of Gelfand's book \cite{gelfand}. It contains a more thorough treatment and results on generalized eigenvectors of self-adjoint operators.

\begin{definition}
A \emph{rigged Hilbert space} is a triple $(\Phi,\hh,\Phi^*)$ such that $\hh$ is a Hilbert space, $\Phi$ is its dense subspace endowed with a topology stronger than the induced one from $\hh$, and $\Phi^*$ is the space of continuous complex linear functionals on $\Phi$.
\end{definition}
One might also take the space $\Phi^\times$ of continuous complex antilinear functionals (which is done, e.g., in \cite{antoine}). If we do so, then we can view $\hh$ as a linear subspace of $\Phi^\times$.

\emph{Why? Here is why:} as I understood from our conversations, rigged Hilbert spaces might be helfpul when we deal with unbounded operators. For instance, the Heisenberg principle suggests that either the position $q$ or the momentum operator $p$ is unbounded; if it happens that, say, $q$ is unbounded, it may have empty point spectrum (which means that the model does not contain information about the position of particles). With a certain rigged Hilbert space $(\Phi,\hh,\Phi^\times)$, we might extend $q$ to $\Phi^\times$, where it will have a non-empty point spectrum. Also, when the Hamiltonian is unbounded but defined on $\Phi$, then every state of $\Phi$ has "finite energy". Usually, $\Phi$ is obtained as the common invariant subspace of a family of distinguished observables. The only warning here is that sometimes, when observables are extended to $\Phi^\times$, their spectra might change. In some cases it's desirable, in some cases it's not, one needs to take this into account when employs the RHS formalism.
\begin{quest}
Given any rigged Hilbert space $(\Phi,\hh,\Phi^\times)$, is it true that $\hh$ is dense in $\Phi^\times$? It is true in examples, but how to show for an abstract space? If $\imath : \Phi \rightarrow \hh$ is the inclusion map, then we obtain a map $\imath^\times : \hh^\times \rightarrow \Phi^\times$. Then $\hh$ can be viewed as a linear subspace of $\Phi^\times$ via $h \mapsto \imath^\times\psi_h$, where $\psi_h(\varphi) = (h,\varphi)$ and $(,)$ is the Hermitian inner product on $\hh$ antilinear in the first slot.
\end{quest}

\begin{definition}
Let $(\Phi, \hh, \Phi^*)$ be a rigged Hilbert space and $A : \Phi \rightarrow \hh$ be a linear operator. An element $f \in \Phi^*$ is called a \emph{generalized eigen-vector} of $A$ if\footnote{I do not use $A^*$, for it goes from $\hh^*$ to $\Phi^*$ and thus its domain may not include every functional from $\Phi^*$. It's probably a subtle moment. If we demanded $A(\Phi) \subseteq \Phi$, then we would be able to switch to $A^*$, but this just doesn't cover all examples we want.} $f(A\varphi) = \lambda f(\varphi)$ for all $\varphi \in \Phi$. In this case, $\lambda$ is called a \emph{generalized eigen-value} of $A$.
\end{definition}
\begin{example}
One example of a rigged Hilbert space is the triple $(S,L^2(\mathbb R), S^*)$, where $S$ is the Schwartz space and $S^*$ is the space of distributions correspondingly. For a fixed $h \neq 0$, consider a unitary operator $U_h(f) (x) := f(x-h)$. Then $U_h$ does not have eigen-vectors\footnote{I do not understand Gelfand's argument. It relies on applying the classical Fourie transform, but there's no formula for it in $L^2(\mathbb R)$, only in $L^1(\mathbb R)$, so there still might be an eigenvector in $L^2(\mathbb R) \setminus L^1(\mathbb R)$. So, if we assume that $f \in L^1(\mathbb R) \subset L^2(\mathbb R)$ is an eigen-vector of $U_h$, then $f(x-h) = \lambda f(x)$ for every $x \in \mathbb R$. But the Fourie transform yields $e^{-ihx}F(x) = \lambda F(x)$, so $F(x) \equiv 0$ (since it's for any $h$) and hence $f(x) \equiv 0$.} in $L^2(\mathbb R)$. However, if we view $U_h$ as an operator on the space of distributions $S^*$, where $S$ is the Schwartz space, then the distributions $x \mapsto e^{i\lambda x}$ are generalized eigen-vectors of $U_h$, for
\[
(e^{i\lambda x},U_h\varphi) = \int_{\mathbb R} e^{i\lambda x} \varphi(x-h)dx = e^{i\lambda h} \int_{\mathbb R}e^{i\lambda x} \varphi(x) dx = e^{i\lambda h}(e^{i\lambda x},\varphi),
\]
where $\varphi \in S$, and the pairing is the usual one between $S$ and $S^*$. 
\end{example}
\begin{definition}
(From Gelfand's book \cite{gelfand}) Let $A : \Phi \rightarrow \hh$ be a linear operator and let $\Phi_{\lambda}^\prime$ be the set of generalized eigen-vectors of $A$ that correspond to a value $\lambda$. With an element $\varphi \in \Phi$ and the value $\lambda$, we associate a functional $\tilde{\varphi}_{\lambda} : \Phi_{\lambda}^\prime \rightarrow \mathbb C$ such that $\tilde{\varphi}_{\lambda}(F_{\lambda}) = F_{\lambda}(\varphi)$. The map $\varphi \mapsto \tilde{\varphi}_{\lambda}$ is called the \emph{spectral decomposition of $\varphi$ with respect to the operator $A$}. We say that the set of generalized eigen-vectors of $A$ is \emph{complete} if the condition $\tilde{\varphi}_{\lambda} \equiv 0$ implies $\varphi = 0$.
\end{definition}
\begin{example}
The set of generalized eigen-vectors\footnote{I don't know why the functions $x \mapsto e^{i\lambda x}$ exhaust the genearlized eigen-vectors. Might think about it later.} of $U_h$ is complete, for the expression $F_{\lambda}(\varphi)$ is, up to a constant, the Fourie transform of $\varphi$. This is the consequence of Plancherel's theorem (or the fact that the Fourie transfrom is an isometry when viewed as an operator $L^2(\mathbb R) \rightarrow L^2(\mathbb R)$.
\end{example}
A theorem of interest for us, drawn from \cite{gelfand}:
\begin{theorem}
Any (possibly unbounded) self-adjoint operator has a complete set of generalized eigen-vectors with real eigen-values.
\end{theorem}
%\begin{lemma}
%If $(\Phi,\hh,\Phi^\times)$ is a rigged Hilbert space, then $\mathcal H$ is dense in $\Phi^\times$.
%\end{lemma}
%\begin{proof}
%We have a continuous linear embedding $\imath : \Phi \rightarrow \hh$, which dualizes to $\imath^\times : \hh^\times \rightarrow \Phi^\times$. Let $(,)$ be the Hermitian inner product antilinear in the first argument. Then $\hh$ can be viewed as a linear subspace of $\Phi^\times$ via $h \mapsto \imath^*\psi_h$, where $\psi_h(\varphi) = (h,\varphi)$.
%\end{proof}